Model Checking Differentially Private Properties

### 2018-01-30 examples.tex
fix graphs

\begin{example}\label{exa:survey}
  Figure~\ref{figure:2-dp} shows the survey
mechanism and its corresponding Markov chain. In the figure, the states
$+$ and $-$ denote the diagnoses are positive or negative
respectively; the states $Y$ and $N$ denote answers to the survey
question. We have $AP=\{Y,N\}$, $L(Y)=\{Y\}$, $L(N)=\{N\}$, and $L(+)=L(-)=\emptyset$. States $+$ and $-$ are neighbors. 
The random noise boosts the probability of answering
\textit{Yes} or \textit{No} to at least $1/4$ regardless of
diagnoses. Inferences on individual diagnosis can be plausibly denied.
{In general, we omit a special state $\dagger$ with $L(\dagger)=\emptyset$, and all omitted transitions in the picture lead to this state.}
\end{example}

@@

The \emph{truncated $\alpha$-geometric mechanism over $\underline{n}$}
outputs $f (x) + Z$ where $Z$ is a random variable with the following
distribution:
\[
\Pr[Z = z] =
\left\{
  \begin{array}{ll}
    0 & \textmd{ if } z < - f (x) \\
    \frac{\alpha^{f (x)}}{1 + \alpha} & \textmd{ if } z = -f (x)\\
    \frac{1 - \alpha}{1 + \alpha}\alpha^{|z|} &
    \textmd{ if } -f (x) < z < n - f (x)\\
    \frac{\alpha^{n - f (x)}}{1 + \alpha} & \textmd{ if } z = n-f (x)\\
    0 & \textmd{ if } z > n - f (x)
  \end{array}
\right.
\]
Note the range of the truncated $\alpha$-geometric mechanism is
$\underline{n}$. The truncated $\alpha$-geometric mechanism is
again oblivious; it is also $(- {\Delta (f)} \ln \alpha, 0)$-differentially
private for any query $f$ with sensitivity $\Delta (f)$.
The truncated $1/2$-geometric mechanism over $\underline{5}$ is
given in Figure~\ref{figure:geometric-mechanism-table}.

@@

\begin{example}
Let the state $in_k$ and $out_l$
denote the input value $k$ and output value $l$ respectively. Define
the state set $S = \{ in_k, out_k : k \in \underline{n} \}$.
The probability transition $\wp (in_k, out_l)$ is the probability of the
output value $l$ on the input value $k$ as defined in the
mechanism. Figure~\ref{figure:geometric-mechanism-markov-chain} gives
the Markov chain of the truncated
$1/2$-geometric mechanism over $\underline{5}$. Further, assume
$L(out_i) = \{ out_i \}$ and $\Delta (f) = 1$. Then $in_k$ and $in_l$ are
neighbors iff $| k - l | \leq 1$.
\end{example}

@@

We consider the database set $D = \{0,1,2,3,4,5\}$, a threshold $t \in \{0,1,2,3,4,5\}$, queries $\{f| f $ with sensitivity $\Delta (f) = 1 \}$. In order to protect privacy, a truncated $1/2-$geometric mechanisms over $\underline{5}$ is applied to each query and the threshold, and what we observe is the first time that a query result is greater than or equal to the threshold after interference. We are interested in the differential privacy property of the data in $D$, assuming that they are all neighbours. The modeling can be done in guarded command language and some fragments are shown below.\todo{the algorithm seems redundant}

>>>>

\begin{example}\label{exa:survey}
  Figure~\ref{figure:2-dp} shows the survey
mechanism and its corresponding Markov chain. In the figure, the states
$+$ and $-$ denote the diagnoses are positive or negative
respectively; the states $Y$ and $N$ denote answers to the survey
question. For each state $s$, we associate an atomic predicate
$\mathit{at}_s$ (not shown in the figure).
States $+$ and $-$ are neighbors. 
The random noise boosts the probability of answering
\textit{Yes} or \textit{No} to at least $1/4$ regardless of
diagnoses. Inferences on individual diagnosis can be plausibly denied.
In general, missing transitions (such as those from $Y$ and $N$) lead
to a special state $\dagger$ with a self-loop. We omit the transitions
and the state $\dagger$ for clarity.
\end{example}

@@

The \emph{truncated $\alpha$-geometric mechanism over $\{ 0, 1,
  \ldots, n \}$}
outputs $f (x) + Z$ where $Z$ is a random variable with the following
distribution:
\[
\Pr[Z = z] =
\left\{
  \begin{array}{ll}
    0 & \textmd{ if } z < - f (x) \\
    \frac{\alpha^{f (x)}}{1 + \alpha} & \textmd{ if } z = -f (x)\\
    \frac{1 - \alpha}{1 + \alpha}\alpha^{|z|} &
    \textmd{ if } -f (x) < z < n - f (x)\\
    \frac{\alpha^{n - f (x)}}{1 + \alpha} & \textmd{ if } z = n-f (x)\\
    0 & \textmd{ if } z > n - f (x)
  \end{array}
\right.
\]
Note the range of the truncated $\alpha$-geometric mechanism is
$\{ 0, 1, \ldots, n \}$. The truncated $\alpha$-geometric mechanism is
again oblivious; it is also $(- {\Delta (f)} \ln \alpha, 0)$-differentially
private for any query $f$ with sensitivity $\Delta (f)$.
The truncated $1/2$-geometric mechanism over $\{ 0, 1, \ldots, 5 \}$ is
given in Figure~\ref{figure:geometric-mechanism-table}.

@@

\begin{example}
Let the state $in_k$ and $out_l$
denote the input value $k$ and output value $l$ respectively. Define
the state set $S = \{ in_k, out_k : k \in \{ 0, 1, \ldots, n \} \}$.
The probability transition $\wp (in_k, out_l)$ is the probability of the
output value $l$ on the input value $k$ as defined in the
mechanism. Figure~\ref{figure:geometric-mechanism-markov-chain} gives
the Markov chain of the truncated
$1/2$-geometric mechanism over $\{ 0, 1, \ldots, 5 \}$. Assume
$\Delta (f) = 1$. Then $in_k$ and $in_l$ are
neighbors iff $| k - l | \leq 1$.
\end{example}

@@

We consider the database set $D = \{0,1,2,3,4,5\}$, a threshold $t \in \{0,1,2,3,4,5\}$, queries $\{f| f $ with sensitivity $\Delta (f) = 1 \}$. In order to protect privacy, a truncated $1/2-$geometric mechanisms over $\{ 0, 1, \ldots, 5 \}$ is applied to each query and the threshold, and what we observe is the first time that a query result is greater than or equal to the threshold after interference. We are interested in the differential privacy property of the data in $D$, assuming that they are all neighbours. The modeling can be done in guarded command language and some fragments are shown below.\todo{the algorithm seems redundant}
